Evaluating machine translation for assimilation via a gap-filling task

### 2015-04-13 2015-eamt-assim/2015-eamt-assim.tex
Added interpretation of Alpha values and a file with individual scores by each task mode (to calculate significance)
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59756 72bbbca6-d526-0410-a7d9-f06f51895060

% actually, I think the following paragraph may be about kappa, will check once I get access to landis77
%The interpretation of Krippendorff's alpha varies depending on the application. One of the general guidelines suggested by \citet{landis77} is as follows (cited after \citet{carletta97}: "[values of alpha] < 0 ``poor'' agreement, 0 to .2 ``slight'', .21 to .40 ``fair'', .41 to .60 ``moderate'', .61 - .80 ``substantial'', and .81 to 1 ``near perfect''"

>>>>

The interpretation of Krippendorff's alpha varies depending on the application. One of the general guidelines suggested by \citet{landis77} for kappa-like measures (which includes Krippendorff's Alpha) is as follows: k < 0.00 indicates ``poor'' agreement, 0.00 to 0.20 ``slight'', 0.21 to 0.40 ``fair'', 0.41 to 0.60 ``moderate'', 0.61 to 0.80 ``substantial'', and 0.81 to 1.00 ``near perfect''.
